Ore Polynomials in Sage

### 2013-06-13 paper/main.tex
text for gcrd and lclm. some changes to normalize() so that leading sign is + added message when improvedPRS fails

\begin{sageexample}
  sage: load("ore_algebra.py", "guessing.py");  #### TO BE FIXED ####
  sage: R.<x> = PolynomialRing(ZZ); A.<Dx> = OreAlgebra(R)
  sage: A
  sage: A.random_element()
  sage: Dx*x
  sage: B.<Sx> = OreAlgebra(R)
  sage: B
  sage: Sx*x
\end{sageexample}

@@

\subsection{gcrd and lclm?}

-- options for selecting algorithms / remainder sequence

-- cite max's paper

-- available for all (univariate) algebras

-- conceptually the base ring is always a field, even when it's not.

>>>>

\begin{sageexample}
  sage: load("ore_algebra.py", "guessing.py", "ore_operator.py");  #### TO BE FIXED ####
  sage: R.<x> = PolynomialRing(ZZ); A.<Dx> = OreAlgebra(R)
  sage: A
  sage: A.random_element()
  sage: Dx*x
  sage: B.<Sx> = OreAlgebra(R)
  sage: B
  sage: Sx*x
\end{sageexample}

@@

\subsection{gcrd and lclm}

A univariate Ore algebra over a field is a left Euclidean domain, which means that it is possible to perform 
left division with remainder. Building upon this, the greatest common right divisor (GCRD) and the least common 
left multiple (LCLM) of two Ore polynomials can be computed. The package provides a number of methods to carry 
out these tasks

\begin{center}
  \begin{tabular}{|l|p{.55\hsize}|}
    \hline
    Method name & short description \\\hline
    \verb|quo_rem(B)| & returns the left quotient and the left remainder of $A$ and $B$.\\
    \verb|gcrd(B)| & returns the greatest common right divisor of $A$ and $B$.\\
    \verb|xgcrd(B)| & returns the greatest common right divisor of $A$ and $B$ and the according B\'ezout coefficients.\\
    \verb|lclm(B)| & returns the least common left multiple of $A$ and $B$.\\\hline
  \end{tabular}
\end{center}

All these methods are also available for Ore operators living in univariate Ore algebras over a base ring $R$ which 
does not necessarily have to be a field. The operators are then implicitly assumed to live in the respective Ore 
algebra over the quotient field $K$ of $R$. The output will be the GCRD (LCLM, quotient, remainder) in the Ore 
algebra over $K$ but not over $R$, in which these objects might not exist or might not be computable.

\begin{sageexample}
  sage: A = OreAlgebra(ZZ['n'], 'Sn');                                           
  sage: G,L1,L2 = A.random_element(2),A.random_element(7),A.random_element(5)    
  sage: while not L1.gcrd(L2)==1: L2 = A.random_element(5)                       
  sage: L1,L2 = L1*G,L2*G                                                        
  sage: (L3,S,T) = L1.xgcrd(L2)                             
  sage: (S*L1+T*L2).normalize() == L3.normalize() == G.normalize()
  sage: LCLM = L1.lclm(L2)
  sage: LCLM.quo_rem(L1)[1] == LCLM.quo_rem(L2)[1] == A.zero()
\end{sageexample}

There are a number of options to adjust the functionality of the methods. For example, the efficiency of computing the GCRD 
depends on the size of the coefficients of intermediate results and there are different strategies to control this in so called 
polynomial remainder sequences (PRS). The default is the improved PRS described in \cite{jaroschek13b}. which will usually be 
the fastest choice.

\begin{sageexample}
  sage: A = OreAlgebra(ZZ['n'], 'Sn');                                           
  sage: L1,L2 = A.random_element(3),A.random_element(2)    
  sage: L1.gcrd(L2, prs=__primitivePRS__)
  sage: L1.gcrd(L2, prs=__classicPRS__)
\end{sageexample}
